Package Interconnection

### 2021-09-12 paper/package_interconnection.Rmd
Add faceted network graph.

pkg_nodes_active <- aut_gr %>%
  mutate(first_author = case_when(first_aut == "Ulrike Groemping" ~ "Ulrike Groemping",
                                 first_aut == "John Lawson" ~ "John Lawson",
                                 first_aut == "Robert B. Gramacy" ~ "Robert B. Gramacy",
                                 first_aut == "Ernesto Barrios" ~ "Ernesto Barrios",
                                 first_aut == "Kevin Wright" ~ "Kevin Wright",
                                 first_aut == "Shwetank Lall" ~ "Shwetank Lall",
                                 n == 1 ~ "Other")) %>%
  mutate(first_author = factor(first_author, levels = c("Ulrike Groemping",
                                                        "John Lawson",
                                                        "Robert B. Gramacy",
                                                        "Ernesto Barrios",
                                                        "Kevin Wright",
                                                        "Shwetank Lall",
                                                        "Other"))) %>%
  select(L2, first_author)

# create igraph object
routes_igraph <- graph_from_data_frame(d = pkg_edges, vertices = pkg_nodes_active, directed = TRUE)

@@

# create the nodes for interactive network
nodes <- pkg_nodes_active %>%
  rowid_to_column("id") %>%
  rename(label = L2) %>%
  mutate(font.size = 25)

@@

Interaction between packages could indicate of how developers utilize the functionality of one or more packages to create new features in their packages. According to @StanstrupJan2019TmTi, dependency and connectivity in terms of reusing codes and inheriting objects could reflect a well-connected and interacting community. In this paper, we observe the interaction limited to only between packages that are listed as DoE packages. Further, the type of interaction include the depended, imported, and suggested packages. Out of `r nrow(pkg_tidy)`, there are only `r nrow(pkg_nodes_active)` packages that interplay each other. To observe these interaction, we use network visualisation using `igraph` [@igraph], `tidygraph` [@tidygraph], and `ggraph` [@ggraph].

@@

pkg_nodes_static <- aut_gr %>%
  mutate(first_author = case_when(first_aut == "Ulrike Groemping" ~ "Ulrike Groemping",
                                 first_aut == "John Lawson" ~ "John Lawson",
                                 first_aut == "Robert B. Gramacy" ~ "Robert B. Gramacy",
                                 n <=2 ~ "Other")) %>%
  mutate(first_author = factor(first_author, levels = c("Ulrike Groemping",
                                                        "John Lawson",
                                                        "Robert B. Gramacy",
                                                        "Other"))) %>%
  select(L2, first_author)

# create igraph object
routes_igraph_static <- graph_from_data_frame(d = pkg_edges, vertices = pkg_nodes_static, directed = TRUE)

# create the input based on the igraph object
routes_tidy_static <- routes_igraph_static %>% as_tbl_graph() %>%
  activate(edges)

# create the graph
ggraph(routes_tidy_static, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  scale_color_manual(values = c("blue", "grey50", "tomato", "magenta")) +
  theme_graph()
```

>>>>

pkg_nodes <- aut_gr %>%
  mutate(first_author = case_when(first_aut == "Ulrike Groemping" ~ "Ulrike Groemping",
                                 first_aut == "John Lawson" ~ "John Lawson",
                                 first_aut == "Robert B. Gramacy" ~ "Robert B. Gramacy",
                                 first_aut == "Ernesto Barrios" ~ "Ernesto Barrios",
                                 first_aut == "Kevin Wright" ~ "Kevin Wright",
                                 first_aut == "Shwetank Lall" ~ "Shwetank Lall",
                                 n == 1 ~ "Other")) %>%
  mutate(first_author = factor(first_author, levels = c("Ulrike Groemping",
                                                        "John Lawson",
                                                        "Robert B. Gramacy",
                                                        "Ernesto Barrios",
                                                        "Kevin Wright",
                                                        "Shwetank Lall",
                                                        "Other"))) %>%
  select(L2, first_author)

# create igraph object
routes_igraph <- graph_from_data_frame(d = pkg_edges, vertices = pkg_nodes, directed = TRUE)

@@

# create the nodes for interactive network
nodes <- pkg_nodes %>%
  rowid_to_column("id") %>%
  rename(label = L2) %>%
  mutate(font.size = 25)

@@

Interaction between packages could indicate of how developers utilize the functionality of one or more packages to create new features in their packages. According to @StanstrupJan2019TmTi, dependency and connectivity in terms of reusing codes and inheriting objects could reflect a well-connected and interacting community. In this paper, we observe the interaction limited to only between packages that are listed as DoE packages. Further, the type of interaction include the depended, imported, and suggested packages. Out of `r nrow(pkg_tidy)`, there are only `r nrow(pkg_nodes)` packages that interplay each other. To observe these interaction, we use network visualisation using `igraph` [@igraph], `tidygraph` [@tidygraph], and `ggraph` [@ggraph].

@@

# create the graph
ggraph(routes_tidy, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(2, 'mm')), 
                 end_cap = circle(2, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 3.1) +
  scale_color_manual(values = c("blue", "tomato", "magenta", "grey50", "#48C9B0", "#C0392B", "#F1C40F")) +
  theme_graph() 
```

```{r, fig.width=12, fig.height = 6}

pkg_nodes_facet <- pkg_nodes %>%
  filter(first_author %in% c("Ulrike Groemping", "John Lawson", "Robert B. Gramacy"))

pkg_edges_facet <- pkg_edges %>%
  filter(L2 %in% pkg_nodes_facet$L2 &
           pkg %in% pkg_nodes_facet$L2)

routes_igraph_facet <- graph_from_data_frame(d = pkg_edges_facet, 
                                             vertices = pkg_nodes_facet, 
                                             directed = TRUE)

# # create the input based on the igraph object
routes_tidy_facet <- routes_igraph_facet %>% as_tbl_graph() %>%
  activate(edges)

ggraph(routes_tidy_facet, layout = "kk") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3.5) +
  theme_graph() +
  facet_nodes(~first_author) +
  scale_color_manual(values = c("tomato", "#48C9B0", "#F1C40F"), guide = "none") +
  th_foreground(foreground = "grey80",  border = TRUE) 
```
